Hierarchical Reverberation Mapping

### 2013-11-01 Paper/ms.tex
Updated a number

We demonstrated this approach on a simulated data set consisting of 100 AGN
with well-measured continuum light curves but sparsely measured (two epochs per
AGN) broad line light curves. For the simulated data set we were able to obtain
an inference on $\mu$, a hyperparameter describing the typical value of the lag,
to within 0.033 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
function had a FWHM of $\sim$ 0.25 dex. This is possible because a subset of
the objects in the sample will have a measureable lag. We hope this approach
will facilitate informative studies of samples of AGN.

>>>>

We demonstrated this approach on a simulated data set consisting of 100 AGN
with well-measured continuum light curves but sparsely measured (two epochs per
AGN) broad line light curves. For the simulated data set we were able to obtain
an inference on $\mu$, a hyperparameter describing the typical value of the lag,
to within 0.047 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
function had a FWHM of $\sim$ 0.25 dex. This is possible because a subset of
the objects in the sample will have a measureable lag. We hope this approach
will facilitate informative studies of samples of AGN.
